A fast algorithm for computing best response strategies in two-person sequential games

### 2014-07-26 paper.tex
more

Furthermore, $F^*$ and $G$ are convex l.s.c, with resolvent (a.k.a \textit{proximity}) operators given by the simple formulae:
\begin{equation}
  \left.
  \begin{aligned}
    (1 + \tau \partial G)^{-1} = \Pi_{\mathbb{R}_+^n}: x \mapsto (x)_+\\
    (1 + \sigma \partial F^*)^{-1}: (y, \zeta) \mapsto (y_0, \zeta + \sigma e)
  \end{aligned}
  \right\}
\end{equation}

>>>>

Furthermore, one easily checks that $F^*$ and $G$ are \textit{proper} convex l.s.c, with resolvent
(a.k.a \textit{proximity}) operators given by the simple formulae:
\begin{equation}
  \left.
  \begin{aligned}
    (1 + \tau \partial G)^{-1} = \Pi_{\mathbb{R}_+^n}: x \mapsto (x)_+\\
    (1 + \sigma \partial F^*)^{-1}: (y, \zeta) \mapsto (y_0, \zeta + \sigma e)
  \end{aligned}
  \right\}
\end{equation}

\begin{remark}
Equation \eqref{eq:pd_opt} is the form of equation (2) in \cite{chambolle2010} if we take $X := \mathbb{R}^n$ and
$Y := \mathbb{R}^m \times \mathbb{R}^p$.
\end{remark}
